---
title: "Predicting Exercise Correctness by Accelerometer Device"
author: "J.E. Turcotte"
date: "June 11, 2016"
output: html_document
---

```{r loading and labelling the data, message=F, warning=F, echo=FALSE}
library(ggplot2)
library(grid)
library(gridExtra)
library(knitr)
library(pander)
library(car)
```
```{r get the data}
training <- read.csv("data/pml-training.csv")
testing <- read.csv("data/pml-testing.csv")
```

## Executive Summary

Six young health participants were asked to perform one set of 10 repetitions of the Unilateral Dumbbell Biceps Curl in five different fashions: exactly according to the specification (Class A), throwing the elbows to the front (Class B), lifting the dumbbell only halfway (Class C), lowering the dumbbell only halfway (Class D) and throwing the hips to the front (Class E).

## Data Repair

```{r normalizing test data, echo=FALSE}
normalize_type <- function(df1,df2) {
     for (vn in names(df1)) {
          if (vn %in% colnames(df1) & vn %in% colnames(df2)) { 
               if (typeof(df2[[vn]]) != typeof(df1[[vn]])) { 
                    if (typeof(df2[[vn]]) %in% c('double','numeric')) {
                         df1[[vn]] <- as.numeric(df1[[vn]])
                    } else if (typeof(df2[[vn]]) == 'integer') {
                         df1[[vn]] <- as.integer(df1[[vn]])
                    } else if (typeof(df2[[vn]]) == 'factor') {
                         df1[[vn]] <- as.factor(df1[[vn]])
                    }
               }
          }
     }
     df1
}

how_na <- function(df,vn){ sum(is.na(df[[vn]])*1) / length(df[[vn]]) }

mostly_na <- function(df,thresh=0.9) {
     na_list <- c()
     for(vn in names(df)) {
          na_ratio <- how_na(df,vn)
          if (na_ratio >= thresh){
               na_list <- c(na_list,vn)
          }
     }
     na_list
}

simpler_formula <- as.formula(paste("classe ~ . -", paste(mostly_na(validation),collapse=" - ")))
```

## Assumptions

* TBD
* TBD
* TBD

## Examining the Data

TBD

## Defining our Model

typical model for binary/multiclass data
build an odd numbr of models
predict with each
predict the class by majority vote

## Source

Ugulino, W.; Cardador, D.; Vega, K.; Velloso, E.; Milidiu, R.; Fuks, H. Wearable Computing: Accelerometers' Data Classification of Body Postures and Movements. Proceedings of 21st Brazilian Symposium on Artificial Intelligence. Advances in Artificial Intelligence - SBIA 2012. In: Lecture Notes in Computer Science. , pp. 52-61. Curitiba, PR: Springer Berlin / Heidelberg, 2012. ISBN 978-3-642-34458-9. DOI: 10.1007/978-3-642-34459-6_6. 
Cited by 2 (Google Scholar)

## Appendix

TBD

