---
title: "Predicting Exercise Correctness by Accelerometer Device"
author: "J.E. Turcotte"
date: "June 11, 2016"
output: html_document
---

```{r loading and labelling the data, message=F, warning=F, echo=FALSE}
library(ggplot2)
library(grid)
library(gridExtra)
library(knitr)
library(pander)
library(car)
```
```{r get the data}
training <- read.csv("data/pml-training.csv")
testing <- read.csv("data/pml-testing.csv")
```

## Executive Summary

TBD

## Assumptions

* TBD
* TBD
* TBD

## Examining the Data

TBD

## Defining our Model

TBD

## Source
Henderson and Velleman (1981), *Building multiple regression models interactively*. Biometrics, 37, 391–411.
\newpage

## Appendix
```{r modifying the data for comprehensibility, echo=FALSE}
cars <- mtcars
colnames(cars) <- c('MPG','cylinders','displacement','horsepower','rear axle ratio','tons','quarter mile','vs','manual','gears','carburetors')
cars$tons <- cars$tons / 2;
```
### Figure 1 - Some of the data
```{r first look at the data, eval=TRUE, echo=FALSE}
pander(head(mtcars[,!names(mtcars) %in% c('vs','qsec')]))
```

### Figure 2 - Summary of data after retitling
```{r studying the data, eval=TRUE, echo=FALSE}
pander(summary(cars[,c('MPG','cylinders','horsepower','tons','manual')]))
```

### Figure 3 - A simple bionomial regression
```{r simple binomial fit, eval=TRUE, echo=FALSE, fig.width=9, fig.height=3}
simple <- ggplot(cars,aes(MPG,manual))
simple <- simple + geom_point(aes(col=as.factor(cylinders), size=tons), alpha=0.5)
simple <- simple + stat_smooth(method="glm", method.args=list(family="binomial"), se=F)
simple + labs(x="Miles per Gallon", y="Manual Transmission")
```
\newpage

### Figures 4 - Simple Linear Model
```{r simple linear model, eval=TRUE, echo=FALSE}
sfit <- lm(MPG ~ manual, cars)
pander(coef(summary(sfit)))
```
This regression suggests that your typical automatic will average about 17.15 miles per gallon, with your average manual transmission vehicle will clock it at over 24 miles per gallon.  But...

### Figure 5 - Multivariate Linear Model
```{r multivariate model, eval=TRUE, echo=FALSE}
mfit <- lm(MPG ~ manual + cylinders + horsepower + I(tons - mean(tons)), cars)
pander(coef(summary(mfit)))
```
Instead, shifting our intercept to that of the average weight vehicle, and regressive for cylinders, horsepower, and tonnage, we get a completely different picture, showing that after other factors are consider, very little detectable increase based on transmission alone remains.

### Figures 6, 7, 8 - Individaulized Residual Plots
```{r plot the residuals of transmission, eval=TRUE, echo=FALSE, fig.width=9, fig.height=5}

grid_arrange_shared_legend <- function(...) {
    plots <- list(...)
    g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
    lheight <- sum(legend$height)
    grid.arrange(
        do.call(arrangeGrob, lapply(plots, function(x)
            x + theme(legend.position="none"))),
        legend,
        ncol = 1,
        heights = unit.c(unit(1, "npc") - lheight, lheight))
}

mtm <- ggplot(cars, aes(y=MPG, x=manual)) + geom_point(aes(size=tons, color=cylinders), alpha=.4) + geom_smooth(method=lm)
mtc <- ggplot(cars, aes(y=MPG, x=cylinders)) + geom_point(aes(size=tons, color=cylinders), alpha=.4) + geom_smooth(method=lm)
mtw <- ggplot(cars, aes(y=MPG, x=tons)) + geom_point(aes(size=tons, color=cylinders), alpha=.4) + geom_smooth(method=lm)

grid_arrange_shared_legend(mtm,mtc,mtw)
```
